\subsection{Description}
The first optimisation we were tasked to implement was constant folding for
the binary operator \emph{+[string]}. which means replace \emph{+[string]}
expression where both sides are literals (which could be any literal) into the
value produced by that expression. E.g. if you have the following expression:
\emph{"hello " + "world"}, you can transform it, at compile time, into its
result: \emph{"hello world"}. This means you have one less \emph{+[string]}
operation to do at runtime. It also reduces the code size by a few characters.
\\
There are a few other cases that can be optimised (the double arrow indicates
the transformation done by our constant folding):
\begin{itemize}
  \item \emph{"" + (a: String) =\textgreater a}: if we add the empty String to
any value typing to String then we can simply put the value itself.
  \item \emph{(a + "hello ") + "world") =\textgreater a + "hello world"}: we
can extract the two constant and "flatten" the \emph{+[string]} operation.
  \item \emph{(a + "") + b) =\textgreater a +[string] b}: if the empty string
is between two \emph{+[string]} we can remove it if we make sure the + operator
of the new expression is a \emph{+[string]}.
\end{itemize}


\subsection{Additional remarks}
In most cases the Scala.js compiler will run on the JVM and not bootstrapped in
JavaScript, this introduces a slight issue as the JVM and EcmaScript do not
have the same specifications regarding the String representation of numbers
\cite{ES6}. Our first approach was to implement the EcmaScript specification in
the \emph{OptimizerCore} but the code was huge for those relatively small
cases, thus it was decided not to constant fold numeric literals which would
require the use of that big specification function. \\
In the mean time we had written unit tests for pretty much all cases of the
EcmaScript specification algorithm and suddently the Scala.js testSuite was
always failing when doing the fullOpt but succeeding in fastOpt. It was soon
discovered that the Google Clojure Compiler, also running on the JVM and only
used in the fullOpt mode, had a bug because it did constant folding (in the
JVM) but did not follow the EcmaScript specification for printing numerics!
An issue has been opened on the Clojure Compiler Project and has yet to be
resolved despite a pull request of ours. \cite{googleBug}